Forecasting the black Sigatoka development rate:\\ A comparison of machine learning techniques

### 2017-04-29 methodology.tex
28 abril 2

In the farm 28 Miles 1\% and in La Rita 2.25\% of the data were missing.
%
To fill-in the missing values spline interpolation was used. \TODO{Falta poner una cita de spline interpolation}
%
The data collected did not exhibit outliers.

@@

The evaluation of the techniques under consideration of their
parameter space, was performed in two stages, described below.

\subsubsection{Phase one}

In the phase one, ten-fold-cross-validation on the total set of
machine learning methods under a subset of configurations was evaluated:

@@

\subsubsection{Phase two}

In the second phase, the best configurations obtained in phase one are
used to validate with the last 50 and 100 weeks.

\TODO{Hmm, ¿entonces cuántas/cuáles semanas se usaron para la fase uno?}

>>>>

In the farm 28 Miles 1\% and in La Rita 2.25\% of the data were missing.
%
To fill-in the missing values spline interpolation was used \citet{Alglib2017}.
%
The data collected did not exhibit outliers.

@@

Ten-fold-cross-validation on the total set of
machine learning methods under a subset of configurations was evaluated:

@@
